### 2021-11-24 thesis/tex/ICintro.tex
update

\section{Neutrino detection}
%TODO: Write down detection process. This section should be written carefully. 
% Specify the guys going into NC and CC. 
% First line only true for CC
% In next lines ,detail the detection process (interaction with detector matter osv). 
% Specify which are occurring in tracks and cascades.
We always observe neutrinos indirectly.
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a fermion (which is not another neutrino) exits with altered properties. This fermion is then directly or indirectly detected, 
and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

In this work, we only study the detectors buried within the Antarctic ice by the IceCube collaboration. 
They are of Cherenkov type, which means that they detect 
a charged lepton by its emitted Cherenkov light, produced from its travel through the ice. 
In the case of CC interactions, this charged lepton is directly involved in the interaction with the neutrino, either as 
both incoming and outgoing particles, or as only the outgoing particle in the case of a hadronic CC interaction.
In the case of NC interactions, the flavor of the fermion interacting with the neutrino is unchanged, but energy 
from the neutrino will be transferred to the fermion that violently recoils, later producing a shower of tertiary particles.

@@

\begin{figure}\label{fig:events}
    \begin{center}
        \begin{subfigure}{0.4\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
            \caption{Event classified as cascade}  
            \label{fig:events_cascade}
          \end{subfigure}
        \begin{subfigure}{0.4\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
            \caption{Event classified as track} 
            \label{fig:events_track}
        \end{subfigure}
        \caption{The two event types distinguished in the IceCube detector.}
    \end{center}
\end{figure}

>>>>

\section{Neutrino detection}
\begin{figure}\label{fig:events}
    \begin{center}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/cascade_event.pdf}
            \caption{Event classified as cascade}  
            \label{fig:events_cascade}
          \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
            \centering
            \includegraphics[clip, trim=0cm 0cm 0cm 30cm, width=1\textwidth]{figures/track_event.pdf}
            \caption{Event classified as track} 
            \label{fig:events_track}
        \end{subfigure}
        \caption{The two event types distinguished in the IceCube detector.}
    \end{center}
\end{figure}
We always observe neutrinos indirectly.
Regardless of the type of interaction (charged current via the $W$ boson, or neutral current
via the $Z$), a quark or charged lepton exits with altered properties. In the case of CC interactions, the fermion
gets its flavor and energy changed. In NC interactions, no flavor change can occur, so the fermion leaves with increased energy.
This fermion is then directly or indirectly detected, 
and the properties of the neutrino involved in the 
interaction are then deduced. This deduction will be imperfect, and this introduces complexities that we will handle in Ch.~\ref{ch:ICmethod}.

In this work, we only study the detectors buried within the Antarctic ice by the IceCube collaboration. 
They are of Cherenkov type, which means that they detect 
a fermion by its emitted Cherenkov light, produced from its travel through the ice. 
In the case of CC interactions, this fermion is directly involved in the interaction with the neutrino, either as 
both incoming and outgoing particles, or as only the outgoing particle in the case of a hadronic interaction.
In the case of NC interactions, the flavor of the fermion interacting with the neutrino is unchanged, but energy 
from the neutrino will be transferred to the fermion that violently recoils, later producing a shower of tertiary particles.

@@
